Hydras \& Co.

### 2023-09-04 doc/hydras.tex
fix a latex error
improve chapter-fol.tex
use latex package turnstile
work on chapter-natural-deduction
more acknowledgements

\setmonofont{DejaVu Sans Mono}[Scale=MatchLowercase]
\usepackage{alltt}
\usepackage{multind}
\usepackage{hyperref}
\usepackage{url}
\usepackage{xcolor, fancyvrb, mdframed}
\usepackage{amsmath}
%\usepackage{fancyhdr}
\usepackage{varioref}
\usepackage{synttree, proof, centernot}
%\usepackage[firstpage]{draftwatermark}
\usepackage{verbatim}
\usepackage[note]{marginote}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{dsfont}
\usepackage{float}
\usepackage{threeparttable}
\usepackage{fontspec}
\usepackage{mathtools}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{placeins}
\usepackage{tikz}
\usepackage{tikzsymbols}
\usetikzlibrary{arrows}
\usepackage{graphicx}
\usepackage{amsmath,mathdots,dsfont}
\usepackage{amssymb}
\usepackage{newunicodechar}
\usepackage{theorem}
\usepackage{xspace}
\usepackage{texments}

@@

@@

\title{Hydras \& Co.}
%\pagestyle{fancy}
%\fancyhead{Hydras, Ordinals, \& Co.}
\makeindex{gaiabridge}
\makeindex{coq}
\makeindex{maths}
\makeindex{hydras}
\makeindex{additions}
\makeindex{ackermann}
\begin{document}
\begin{titlepage}
   \begin{center}
       \vspace*{1cm}

@@

       \emph{Pierre Castéran, LaBRI, Univ. Bordeaux, CNRS UMR 5800\\ \textbf{email:} pierre dot casteran arobas gmail dot com. \\ With contributions by Yves Bertot, Ilm\={a}rs C\={i}rulis, \'Evelyne Contejean,  Jérémy Damour, Florian Hatat, Pascal Manoury, Karl Palmskog, Clément Pit-Claudel, and Théo Zimmermann. \\ The formalization of primitive recursive functions and Peano Arithmetic was originally authored by Russel O'Connor.}%\cite{OConnor05}.}

@@

\section{Acknowledgements}
\label{sec:orgheadline5}
    Many thanks to Yves Bertot, Ilm\={a}rs C\={i}rulis, \'Evelyne Contejean, Jéremy Damour,   Florian Hatat,  David Ilcinkas, 
Pascal Manoury,  Karl Palmskog, Cl\'ement Pit-Claudel, Sylvain Salvati, Alan Schmitt and Théo Zimmermann for their help on the elaboration of this library and  document, and to the
 members of the \emph{Formal Methods} team and the \emph{Coq working group} at laBRI for their helpful comments 
on  oral presentations of this work.

@@

% \subsubsection{Links to the Coq source}

@@

\include{chap-intro-goedel}
\include{chapter-primrec} 
\include{chapter-fol}

\include{chapter-encoding}

>>>>

\setmonofont{DejaVu Sans Mono}[Scale=MatchLowercase]
\usepackage{alltt}
\usepackage{multind}
\usepackage{hyperref}
\usepackage{url}
\usepackage{xcolor, fancyvrb, mdframed}
\usepackage{amsmath}
\usepackage{turnstile}
%\usepackage{fancyhdr}
\usepackage{varioref}
\usepackage{synttree, proof, centernot}
%\usepackage[firstpage]{draftwatermark}
\usepackage{verbatim}
\usepackage[note]{marginote}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{dsfont}
\usepackage{float}
\usepackage{threeparttable}
\usepackage{fontspec}
\usepackage{mathtools}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{placeins}
\usepackage{tikz}
\usepackage{tikzsymbols}
\usetikzlibrary{arrows}
\usepackage{graphicx}
\usepackage{amsmath,mathdots,dsfont}
\usepackage{amssymb}
\usepackage{newunicodechar}
\usepackage{theorem}
\usepackage{xspace}
\usepackage{texments}
\usepackage{proof}

@@

\newcommand {\sdash} {\sststile{\mathrm{S}}{}}
\newcommand {\hdash} {\sststile{}{}}

@@

\title{Hydras \& Co.}
%\pagestyle{fancy}
%\fancyhead{Hydras, Ordinals, \& Co.}
\makeindex{gaiabridge}
\makeindex{coq}
\makeindex{maths}
\makeindex{hydras}
\makeindex{additions}
\makeindex{ackermann}

\begin{document}
\begin{titlepage}
   \begin{center}
       \vspace*{1cm}

@@

       \emph{Pierre Castéran, LaBRI, Univ. Bordeaux, CNRS UMR 5800\\ \textbf{email:} pierre dot casteran arobas gmail dot com. \\ With contributions by Yves Bertot, Ilm\={a}rs C\={i}rulis, \'Evelyne Contejean,  Jérémy Damour, St\'ephane Desarzens, Florian Hatat, Pascal Manoury, Karl Palmskog, Clément Pit-Claudel, and Théo Zimmermann. \\ The formalization of primitive recursive functions and Peano Arithmetic was originally authored by Russel O'Connor~\cite{OConnor05}.}

@@

\section{Acknowledgements}
\label{sec:orgheadline5}
    Many thanks to Yves Bertot, Ilm\={a}rs C\={i}rulis, \'Evelyne Contejean, Jéremy Damour,   St\'ephane Desarzens, Florian Hatat,  David Ilcinkas, 
Pascal Manoury,  Karl Palmskog, Cl\'ement Pit-Claudel, Sylvain Salvati, Alan Schmitt and Théo Zimmermann for their help on the elaboration of this library and  document, and to the
 members of the \emph{Formal Methods} team and the \emph{Coq working group} at laBRI for their helpful comments 
on  oral presentations of this work.

@@

%\subsubsection{Links to the Coq source}

@@

\include{chap-intro-goedel}
\include{chapter-primrec} 
\include{chapter-fol}
\include{chapter-natural-deduction}
\include{chapter-lnn-lnt}
\include{chapter-encoding}
